---
output:
  rmarkdown::tufte_handout:
    dev: CairoPDF
    keep_tex: true
title: "Summary"
date: "\\vspace{0 mm}"
header-includes:
  \usepackage{graphicx}
  \usepackage{caption}
  \usepackage{fixltx2e}
  \usepackage{rotating}
documentclass: tufte-handout
classoption: a4paper, sfsidenotes, twoside

bibliography: /home/tom/Dropbox/temp/PapersLib-2015-11-04.bibtex
---

```{r setup, include=FALSE, results="hide"}
library(ggplot2)
theme_slide <- theme_minimal() +
  theme(plot.background = element_rect(fill = "transparent", colour = NA))
knitr::opts_chunk$set(
  dev.args=list(bg = "transparent"),
  echo = FALSE,
  tidy.opts = list(width.cutoff = 32)
  )
```

# Introduction

* Relationship between rice yield and branching complexity
* Relationship between meristem activity / determinancy and branching complexity
* Relationship between gene expression and meristem identity
* Why is control of morphology complex (redundancy, dynamics)? An example to illustrate this.
* **Figure**: panicle morphology during development
\begin{marginfigure}
  \includegraphics{morphology.png}
\end {marginfigure}

# Background

* LMD and RNAseq methodology
    * why LMD was chosen
    * how RNAseq works
    * problems with small amounts of starting material

# Results figures^[How to source `figures.R` and resize without all the data?]

* LMD figure
    * amount of RNA produced
* clusters?
* transcription factor examples
    * ALOG family
    * HB?
* hormone example(s)?
    * cytokinin

\begin{marginfigure}
  \includegraphics{lmdFigure.pdf}
\end {marginfigure}
\begin{marginfigure}
  \includegraphics{/media/tom/cfd04a45-d8e3-4944-a080-6cfef1543df8/home/tom/Documents/writing/lmdPaper/figures/f_mfuzzClusters-1.pdf}
\end {marginfigure}

# Discussion

* modes of expression in meristems:
    * apical vs. axillary
    * transitions in axillary meristems
* characteristics of the different cell types?
* dynamical networks of genes controlling expression (how this specifies the cell types)
* variety in panicle phenotypes in different accessions
* how did the network 

# Code in tufte-handout
```{r plot1, echo = TRUE, fig.margin = TRUE}
df <- data.frame(x = rnorm(10), y = rnorm(10), lab = rep(c("bof1", "bof2"),
                                                         each = 5))
ggplot(df, aes(x = x, y = y, colour = lab)) +
  theme_slide +
  geom_point() +
  scale_color_brewer(palette = "Set1")
```

# References
